Lossy compression of DNA sequencing quality data

### 2016-04-26 bmc_manuscript/manuscript.tex
A bit more polishing of the text for economics of RQS compression.

The economic costs of file size for compression with \textsc{rqs}, in
our interpretation, appear to be the fixed costs of the dictionary of
commonly occurring $k$-mers, and the marginal costs that are the
product of the number of positions of $k$-mers within the chosen
Hamming distance from dictionary $k$-mers times the cost of
representing these positions. It should be noted that the fixed costs
of the dictionary of commonly occurring $k$-mers can be amortized over
reads for which the dictionary may be appropriately used (e.g., reads
from the same species).

>>>>

The economic costs of file size for compression with \textsc{rqs}, in
our interpretation, appear to be the fixed costs of the dictionary of
commonly occurring $k$-mers, and the marginal costs that are the
product of the number of positions of $k$-mers within the chosen
Hamming distance from dictionary $k$-mers times the cost of
representing these positions. As with compression based on profiles,
amortization applies to fixed costs of compression with
\textsc{rqs}. Here the fixed costs of the dictionary of commonly
occurring $k$-mers can be amortized over reads for which the
dictionary may be appropriately used (e.g., reads from the same
species).
